Notes on JNLS paper

### 2019-09-20 paper2_JNLS/notes.tex
NM

I believe that by symmetry $\meanz{\Hthree \Htwo} = 0$
TO CONTINUE

@@

>>>>

I believe that by symmetry $\meanz{\Hthree \Htwo} = 0$
\\ TO CONTINUE

@@

\seclabel{Goal} We need some test problems for which we can compute the Hamiltonian exactly, to make sure it is done correctly in the Matlab DNS and Julia sampling codes.

\seclabel{Test examples} \\
1. $u = b \left( (a+\cos{x})^2 - (a^2+1/2) \right)$ \\
i. The above satisfies $\Mo[u] = 0$ (due to the choice of constant $(a^2 + 1/2)$. \\
ii. The choice $b = \sqrt{ \frac{8}{\pi(1+16 a^2)}}$ satisfies $\En[u] = 1$ \\
Wolfram alpha gives that
\begin{align}
&\Htwo[u] = \frac{1}{2} \int_{-\pi}^{\pi} u_x^2 \dx = 1 + \frac{3}{1+16 a^2} \\
&\Hthree[u] = \frac{1}{6} \int_{-\pi}^{\pi} u^3 \dx = 8 \sqrt{2} \pi a^2 \left( 16 \pi a^2 + \pi \right)^{-3/2}
\end{align}
$\bullet$ I tested the Matlab DNS code and it works! I tested $\Htwo$ and $\Hthree$ separately. Each gave a relative error on the order of machine precision.
